Gravitational Lens Modelling in a Citizen Science Context

### 2014-10-06 text/ms.tex
edits following comments by SM

While we expected the identification of lensed images to be trivial,
given the generally clean appearance of the sims in the test, we
expected the parities and time-ordering to be more difficult.  While
the \spl tutorials had provided some general rules of thumb, to be
consistently correct with the time-ordering, a modeller needs to
develop some intuition for arrival time surfaces.  This is an area
where experience and tutorials training could improve results at a
later stage, and correspondingly, feedback on the difficulties
modellers encounter can help improve the tutorial materials.

>>>>

While we expected the identification of lensed images to be trivial,
given the generally clean appearance of the sims in the test, we
expected the parities and time-ordering to be more difficult.  While
the \spl tutorials had provided general guidelines, to be consistently
correct with the time-ordering, a modeller needs to develop some
intuition for arrival time surfaces.  This is an area where experience
and tutorials training could improve results at a later stage, and
correspondingly, feedback on the difficulties modellers encounter can
help improve the tutorial materials.
